---
title: "ST558 Project2 Blog Post"
author: "Shan Luo"
date: '2022-07-09'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r render, echo = TRUE, eval = FALSE}
rmarkdown::render("/Users/sl666/Desktop/ST558/ShanLLL52.github.io/_Rmd/2022-07-09-ST558Project2Blog-post.Rmd", 
          output_format = "github_document", 
          output_dir = "/Users/sl666/Desktop/ST558/ShanLLL52.github.io/_posts",
          output_options = list(
            html_preview = FALSE))
```

## ST558 Project2 Blog Post  

I will try to use more predictors, fit other different models and compare them to find best one. I think the most difficult and intereting part was to do the automation for other channels. It took a little bit time to figure out how to use the params to filter the corresponding data, but it's really interesting. I learned how to do the automation and learned more about how to use the github. Github is indeed helpful for team work.  

[`ST558Project2 with Github Page`](https://shanlll52.github.io/ST558Project2/)  

[`ST558Project2 Repo itself`](https://github.com/ShanLLL52/ST558Project2)  
