---
title: "ST558 Fifth Blog Post"
author: "Shan Luo"
date: '2022-07-22'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Code for render  

```{r render, echo = TRUE, eval = FALSE}
rmarkdown::render("./_Rmd/2022-07-22-ST558Blog5-post.Rmd", 
          output_format = "github_document", 
          output_dir = "/Users/sl666/Desktop/ST558/ShanLLL52.github.io/_posts",
          output_options = list(
            html_preview = FALSE))
```

I think that I learned a lot about data science in this course and I will continue to use R going forward. Because R is the language that I am most familiar with. Also, R is very convenient and has large user community, which is very helpful when I use R. Now I learned more about machine learning, especially training and test set, and knew a little bit about database as well as shiny app, which are very interesting. I have no idea how it may work in practice, but I believe I am more prepared. I will probably do some practice in database and shiny app. Before taking this course, I had experience in machine learning. After taking this course, I want to explore more about database as well as shiny app.  


